---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)

suppressPackageStartupMessages(library(tidyverse))

logged_data <- read_csv(
  "https://docs.google.com/spreadsheets/d/e/2PACX-1vQlBGNLHIJEcG260DORd1QnqG-7CCSvl1QoX-b5aK0tsE8l1onaDP51CvLc6_JxWoSU4wICqH3PAD5T/pub?gid=1413703802&single=true&output=csv",
  show_col_types = FALSE
)

price <- as.numeric(logged_data[[4]])
opinion <- logged_data[[5]]
decision <- logged_data[[6]]
```

```{css}
body {
  font-family: Arial, sans-serif;
  margin: 20px;
}

h2 {
  color: violet;
}

p {
  font-size: 20px;
}
```

## Current petrol price observations and opinions

This report presents observations of current petrol prices collected over several days.

It focuses on how people felt about the petrol prices they observed and whether those prices affected their decisions.

The average petrol price in this dataset is `r round(mean(price, na.rm = TRUE), 2)` NZD per litre.

The minimum petrol price recorded is `r min(price, na.rm = TRUE)` NZD per litre.

```{r}
ggplot(logged_data, aes(x = opinion)) +
  geom_bar() +
  labs(
    title = "Opinions on current petrol prices",
    x = "Opinion",
    y = "Count"
  )
```

```{r}
ggplot(logged_data, aes(x = decision)) +
  geom_bar() +
  labs(
    title = "Effect of petrol price on decision",
    x = "Decision",
    y = "Count"
  )
```
