---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
suppressPackageStartupMessages(library(tidyverse))
logged_data=read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQlBGNLHIJEcG260DORd1QnqG-7CCSvl1QoX-b5aK0tsE8l1onaDP51CvLc6_JxWoSU4wICqH3PAD5T/pub?gid=1413703802&single=true&output=csv")
#rename the data
latest_data <- logged_data%>%
  rename(
    timestamp = `Timestamp`,
    date = `What date did you observe the petrol price?`,
    location = `Where did you see the petrol price?`,
    price = `What was the petrol price per litre ?`,
    opinion = `How do you feel about the current petrol price?`,
    decision = `Did the petrol price affect your decision ?`
  )
```

```{css}
body {
  font-family: Arial, sans-serif;
  margin: 20px;
}

h2 {
  color: violet;
}

p {
  font-size: 30px;
}
```


## Current petrol price observations and opinions
The data in this report is used to analyze the recent petrol prices.

It focuses on how people felt about the petrol prices they observed and whether those prices affected their decisions.
The average petrol price in this dataset is `r round(mean(latest_data$price), 2)` NZD per litre.

The minimum petrol price recorded is `r min(latest_data$price)` NZD per litre.

```{r}
#chart 1
latest_data %>%
  ggplot(aes(x = opinion)) +
  geom_bar() +
  labs(
    title = "Opinions on current petrol prices",
    x = "Opinion",
    y = "Count"
  )
```
```{r}
#chart 2
latest_data %>%
  ggplot(aes(x = decision)) +
  geom_bar() +
  labs(
    title = "Effect of petrol price on decision",
    x = "Behaviour",
    y = "Count"
  )
```
