---
title: My dynamic report
output: html_fragment
---
```{r setup, include=TRUE} # 暂时改为 TRUE 调试
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)

# 建议加一个 tryCatch 或者检查文件是否存在
url <- "[https://docs.google.com/spreadsheets/d/e/2PACX-1vQlBGNLHIJEcG260DORd1QnqG-7CCSvl1QoX-b5aK0tsE8l1onaDP51CvLc6_JxWoSU4wICqH3PAD5T/pub?gid=1413703802&single=true&output=csv](https://docs.google.com/spreadsheets/d/e/2PACX-1vQlBGNLHIJEcG260DORd1QnqG-7CCSvl1QoX-b5aK0tsE8l1onaDP51CvLc6_JxWoSU4wICqH3PAD5T/pub?gid=1413703802&single=true&output=csv)"

logged_data <- read_csv(url)

# 打印一下列名，确保 rename 不会因为找不到列而死掉
# print(colnames(logged_data))

latest_data <- logged_data %>%
  rename(
    timestamp = 1, # 使用列索引更保险
    date = 2,
    location = 3,
    price = 4,
    opinion = 5,
    decision = 6
  )
```
```{css}
body {
  font-family: Arial, sans-serif;
  margin: 20px;
}
h2 {
  color: violet;
}
p {
  font-size: 30px;
}
```
## Current petrol price observations and opinions
The data in this report is used to analyze the recent petrol prices.
It focuses on how people felt about the petrol prices they observed and whether those prices affected their decisions.
The average petrol price in this dataset is `r round(mean(latest_data$price), 2)` NZD per litre.
The minimum petrol price recorded is `r min(latest_data$price)` NZD per litre.
```{r}
#chart 1
latest_data %>%
  ggplot(aes(x = opinion)) +
  geom_bar() +
  labs(
    title = "Opinions on current petrol prices",
    x = "Opinion",
    y = "Count"
  )
```
```{r}
#chart 2
latest_data %>%
  ggplot(aes(x = decision)) +
  geom_bar() +
  labs(
    title = "Effect of petrol price on decision",
    x = "Behaviour",
    y = "Count"
  )
```
